Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-03 method.tex
Added cpu extrapolation
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@925 ccdd05d5-56c1-461a-bf98-85f6876523b4

\subsubsection{Extrapolation of the computational cost of the \lloid\ method to an Advanced LIGO search}

Table \ref{table:flops} shows that it requires about 0.5 GFLOPS to conduct the
filtering, reconstruction and resampling stages of the \lloid\ method for 657
templates chosen around typical NS--NS mass parameters.  Given the capability
of modern CPUs it should be possible to filter that sub-bank on one CPU.
Assuming that the cost holds for the other sub-banks we expect that the full
parameter space should require $\sim 150$ CPUs for realtime filtering with the
\lloid\ method per detector.  Even if real implementations fall short of these
estimates by factors of several, there will still be ample computing resources
for an early warning search in the advanced detector era.

>>>>

\subsubsection{Extrapolation of the computational cost to an Advanced LIGO search}

Table~\ref{table:flops} shows that the \lloid\ method requires $\sim 10^8$ \flops\
to cover a sub-bank of comprising $\sim 10^2$ out of $\sim 10^5$ sets of intrinsic
source parameters.  Given that modern (ca. 2011) workstations can sustain
computation rates up to $\sim 10^{10}$ \flops{}, and assuming that other regions of the
parameter space have similar computational scaling, an entire search could be implemented
with $\gtrsim 10$ machines.

By comparison, using the \TD\ method to achieve the same latency costs $\sim 10^{13}$ \flops\ for this particular sub-bank, and so it would require $\sim 10^6$ present-day machines.  Presently, the \LIGO\ data grid consists of only $\sim 10^4$ machines.
